Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-04 paper.qmd
Update Figure 3

hex_grid_scurve <- ggplot(
  data = hex_grid_with_counts, 
  aes(x = x, y = y)) +
  geom_polygon(color = "black", 
               aes(group = hex_poly_id), 
               fill = "#ffffff") +
  geom_point(data = umap_scurve_scaled, 
             aes(x = UMAP1, y = UMAP2), 
             alpha = 0.5) +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("b", sc_ltr_pos)
```

>>>>

hex_grid_scurve <- ggplot(
  data = hex_grid_with_counts, 
  aes(x = x, y = y)) +
  geom_polygon(color = "black", 
               aes(group = hex_poly_id), 
               fill = "#ffffff") +
  geom_point(data = umap_scurve_scaled, 
             aes(x = UMAP1, y = UMAP2), 
             alpha = 0.5, size = 0.5) +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("b", sc_ltr_pos)
```
